\section{Quiz or closed questions}
\subsection{General}
\textbf{\\What is a stream cipher?}

\textbf{\\Which of the following defines a cipher text attack?}

\textbf{\\what is known plaintext attack}

\textbf{\\Classification of wireless network, adhoc/infrastructure, fixed/mobile, wwan/wlan}

\subsection*{Wireless Communication}

\textbf{\\In digital Communication system which type of waveforms are propagated in the channel?}

\textbf{\\Order the elements in the transmission chain (encoder, modulator, channel etc.)}

\textbf{\\Why the definition of the bandwidth 3db}

\textbf{\\PSK modulation - about the energy level of symbols and saturation level of a power amplifier}


\subsection{GNSS}
\textbf{\\How can a spoofing attack be detected?}

\textbf{\\Why monitoring GNSS spectrum is insufficient for spoofing detection?}

\textbf{\\GNSS - Why is line of sight to satellites important to have correct pseudorange calculations?}

\textbf{\\Are the clocks of Satellite and receiver synchronized?}

\textbf{\\What is broadcasted by the satellite}

\textbf{\\Do Out-Of-Band interferences affect GNSS?}


\textbf{\\Which of the following is a common indicator of a GNSS spoofing attack?}
\begin{enumerate}
\item A gradual decrease in signal strength over time
\item Enhanced accuracy and reliability of GNSS signals
\item Sudden and significant deviations in position, velocity or time calculations
\item None of the others
\item Discrepancies between GNSS-based positions and those from alternative navigation systems (eg., inertial navigation systems)
\end{enumerate}

\subsection{WLAN / wifi}

\textbf{\\Two devices connected in Wi-Fi without RTS/CTS assumed to collide, order what happened (and there where a series of steps like A sends, B, sends, DATA(A) collide with DATA(B) etc,)}

\textbf{\\Sort the exchanged messages to connect to an AP}

\textbf{\\Algorithm used in OWE}

\textbf{\\How WEP key management ic compared to WPA/WPA2}

\textbf{\\why not csma/ cd in wifi}

\textbf{\\authentication service - in the context of wireless networks}

\textbf{\\CDMA networks - why is power control important?}

\textbf{\\Purpose of DIFS in wifi networks}


\textbf{\\802.11 network - using ISM BW range, how many independent channels can be used?}

\textbf{\\Which wifi protocols are considered secure? (wpa with tkip, wpa2, wep, wpa3 ) }

\textbf{\\ranking throughput higher to lower 802.11g 802.11n using tcp or udp and using or not rts/cts }

\textbf{\\Definition of authenticator supplicant port server authentication}

\textbf{\\Maximum goodput that can be reached with this technology from 1 to 9}
\begin{itemize}
    \item 802.11n, RTS/CTS enabled, UDP+IP
	\item 802.11n, RTS/CTS disabled, UDP+IP
	\item 802.11g, RTS/CTS enabled, UDP+IP
	\item 802.11g, RTS/CTS disabled, UDP+IP
	\item 802.11n, RTS/CTS enabled, TCP+IP
	\item 802.11g, RTS/CTS disabled, TCP+IP
	\item 802.11g, RTS/CTS enabled, TCP+IP
	\item 802.11n, RTS/CTS disabled, TCP+IP
	\item Fast ethernet 100 Mbps
\end{itemize}
	

\subsection{WPAN / Bluetooth}

\textbf{\\How does Bluetooth Classic handle privacy concerns compared to Bluetooth LE?}
\begin{enumerate}
    \item Bluetooth Classic uses encryption keys for all data transmissions.
    \item Bluetooth Classic limits the number of devices that can connect simultaneously 
    \item Bluetooth Classic randomizes MAC addresses for improved privacy.
    \item Bluetooth Classic does not have any privacy features
    \item None of the other options.
\end{enumerate}


\textbf{\\What is bluesnarfing?}

\textbf{\\BT secure services}

\textbf{\\How prevent MITM on Bluetooth Secure Simple Pairing?}

\textbf{\\Which multiple access mechanism BT uses?}


\subsection{WWAN / mobile}

\textbf{\\What is Stingray vulnerability?}

\textbf{\\Which of the following are 2G vulnerabilities?}


\textbf{\\Ss7 vulnerability}


\textbf{\\Purpose of paging and location are in mobile network}


\textbf{\\Differences between VLR and HLR}

\textbf{\\Describe device authentication in GSM (completare l’immagine con le parti date.)}

\textbf{\\4G networks - techniques used to enhance security}

